### 2011-11-19 doc/theses/vitasek/bibliography.tex
Thesis: fixing the bibliography again.

@@

@@

@@

@@

\bibitem[Mak]{mathprog}
Andrew Makhorin.
\newblock GNU Mathprog.
\newblock \url{http://lpsolve.sourceforge.net/5.5/MathProg.htm}.

@@

@@

\bibitem[VMP08]{1802522}
Ond\v{r}ej Vo\v{s}ta, Irena Ml\'{y}nkov\'{a}, and Jaroslav Pokorn\'{y}.
\newblock Even an Ant Can Create An XSD.
\newblock In {\em DASFAA'08: Proceedings of the 13th international conference on Database systems for advanced applications}, pages 35--50, Berlin, Heidelberg, 2008. Springer-Verlag.

>>>>

\bibitem[BDF{\etalchar{+}}00]{fajt-12}
Peter Buneman, Susan Davidson, Wenfei Fan, Carmem Hara, and Wang chiew Tan.
\newblock Reasoning About Keys for XML.
\newblock In {\em Information Systems}, page 2003, 2000.

@@

\bibitem[BLNT07]{fajt-51}
Jana Bauckmann, Ulf Leser, Felix Naumann, and Véronique Tietz.
\newblock Efficiently Detecting Inclusion Dependencies.
\newblock In {\em In Int. Conf. on Data Engineering (ICDE 07}. Poster, 2007.

@@

\bibitem[GZ02]{fajt-39}
G\"{o}sta Grahne and Jianfei Zhu.
\newblock Discovering Approximate Keys in XML Data.
\newblock In {\em Proceedings of the eleventh international conference on Information and knowledge management}, CIKM '02, pages 453--460, New York, NY, USA, 2002. ACM.

@@

\bibitem[JUF10]{fajt-53}
B.~Jana, L.~Ulf, and N.~Felix.
\newblock {\em Efficient and Exact Computation of Inclusion Dependencies for Data Integration}.
\newblock Technische Berichte des Hasso-Plattner-Instituts f{\"u}r Softwaresystemtechnik an der Universit{\"a}t Potsdam. Universit{\"a}tsverlag Potsdam, 2010.

@@

\bibitem[Mak]{mathprog}
Andrew Makhorin.
\newblock GNU MathProg.
\newblock \url{http://lpsolve.sourceforge.net/5.5/MathProg.htm}.

@@

\bibitem[Pas97]{Paschos:1997:SAO:254180.254190}
Vangelis~T. Paschos.
\newblock A Survey of Approximately Optimal Solutions to Some Covering and Packing Problems.
\newblock {\em ACM Comput. Surv.}, 29:171--209, June 1997.

\bibitem[SBHR06]{fajt-41}
Yannis Sismanis, Paul Brown, Peter~J. Haas, and Berthold Reinwald.
\newblock Gordian: Efficient and Scalable Discovery of Composite Keys.
\newblock In {\em In Proc. International Conference on Very Large Data Bases (VLDB}, pages 691--702, 2006.

@@

\bibitem[VMP08]{1802522}
Ond\v{r}ej Vo\v{s}ta, Irena Ml\'{y}nkov\'{a}, and Jaroslav Pokorn\'{y}.
\newblock Even an Ant Can Create an XSD.
\newblock In {\em DASFAA'08: Proceedings of the 13th international conference on Database systems for advanced applications}, pages 35--50, Berlin, Heidelberg, 2008. Springer-Verlag.
